The relative roles of genetic, ecological and environmental factors in species radiations

### 2018-02-20 paper/draft.tex
add some refs in intro, extend disc

%% [NEW ANGLE:]
Islands are understood as suitable model systems for ecology and evolution due to their well definable characteristics like isolation. (e.g., Losos \& Ricklefs 2009) %TODO: ref
While often featuring unique species communities and harboring countless endemics, %TODO: refs
islands are especially threatened by climate change, human impact and invasive species. %TODO: refs
This makes understanding the functioning and evolution of island communities a high priority objective.

@@

>>>>

%% [NEW ANGLE:]
Islands are understood as suitable model systems for ecology and evolution due to their well definable characteristics like isolation. (e.g., Losos \& Ricklefs 2009) %TODO: ref
While often featuring unique species communities and harboring countless endemics, %TODO: refs
islands are especially threatened by climate change, human impact and invasive species (Fordham \& Brook 2010). %TODO: refs
This makes understanding the functioning and evolution of island communities a high priority objective.

@@

In this work we concentrated on genetic influences on speciation.
However, there is ongoing debate on how strongly genetic factors also impact extinction processes (Jamieson 2007).
Seeing that observed speciation rates are in fact net speciation rates highlights the need to mechanistically explore
these processes as well.
In fact, genetic processes might play an important role in the issue of extinction debt. %% cite Ludmilla, ask for refs
